NumPy---Array Computation for Python

### 2019-12-10 paper.tex
Add outline

NumPy is the fundamental array computation library for the Python
ecosystem.  It underpins almost every library that does numerical
computation, including SciPy.  NumPy consists of the `ndarray`-object
along with utility functions to operate on such arrays.  Because of
its inherent simplicity—being a pointer to memory with some
associated meta-data about shape, data-type, and so forth—the NumPy
array has become the {\it de facto} exchange format for array data in
Python.  That said, NumPy has now seen such widespread adoption that
not only the array object but also its {\it Application Programming
  Interface} (API) has become ubiquitous, and is imitated by, e.g.,
popular tensor computation libraries.

@@

While, by 2006, NumPy was already eminently usable, it lacked good
documentation. In order to use NumPy in his classes, Joe Harrington
from the University of South Florida sponsored several rounds of the
NumPy Documentation Marathon [citations].  During these intensive
documentation improvement sessions, a Wikipedia-like system was
developed to allow community members to contribute so-called
``docstrings''—text describing each NumPy function. A community
documentation standard was published so that these pieces of
documentation would all provide similar information, and conform to a
basic standard of quality. Experienced community members reviewed and
integrated contributed docstrings, and soon NumPy had thorough
documentation coverage.

@@

For a more detailed history of the scientific Python ecosystem, please
refer to [SciPy arxiv / nature paper].

>>>>

NumPy\cite{vanderwalt2011numpy} is the fundamental array computation library for the Python
ecosystem \cite{dubois2007guest,oliphant2007python,millman2011python,perez2011python}.
It underpins almost every library that does numerical
computation, including SciPy.  NumPy consists of the `ndarray`-object
along with utility functions to operate on such arrays.  Because of
its inherent simplicity—being a pointer to memory with some
associated meta-data about shape, data-type, and so forth—the NumPy
array has become the {\it de facto} exchange format for array data in
Python.  That said, NumPy has now seen such widespread adoption that
not only the array object but also its {\it Application Programming
  Interface} (API) has become ubiquitous, and is imitated by, e.g.,
popular tensor computation libraries.

@@

While, by 2006, NumPy was already eminently usable, it lacked good
documentation. In order to use NumPy in his classes, Joe Harrington
from the University of South Florida sponsored several rounds of the
NumPy Documentation Marathon \cite{harrington2008scipy,vanderwalt2008scipy}.
During these intensive
documentation improvement sessions, a Wikipedia-like system was
developed to allow community members to contribute so-called
``docstrings''—text describing each NumPy function. A community
documentation standard was published so that these pieces of
documentation would all provide similar information, and conform to a
basic standard of quality. Experienced community members reviewed and
integrated contributed docstrings, and soon NumPy had thorough
documentation coverage.

@@

For a more detailed history of the scientific Python ecosystem, please
refer to ``SciPy 1.0---Fundamental Algorithms for Scientific Computing
in Python'' \cite{virtanen2019scipy}.

\section*{Architecture and implementation choices}

\subsection*{Library organisation}

\subsection*{Common infrastructure}

\subsection*{Language choices}

\section*{Recent technical improvements}

\subsection*{NEPS revived and roadmap}

\subsection*{Random}

\subsection*{\_\_array\_func\_\_}

\subsection*{Testing on multiple architectures}
